Hierarchical Region-Network Sparsity for\\ High-Dimensional Inference in Brain Imaging

### 2016-02-05 paper/icml2016/example_paper.tex
style up 6

The present approach has important advantages over previous
analysis strategies that rely on dimensionality reduction of
the neuroimaging data to harness the curse of dimensionality.
They often resort to preliminary pooling functions within regions
or regression against network templates
for subsequent supervised learning on the aggregated feature space.
Such lossy approaches of
feature engineering and subsequent inference
\textit{i)} can only satisfy the specialization or
integration account of brain organization,
\textit{ii)} depend on the ground truth being a region or network effect,
and
\textit{iii)} cannot issue individual coefficients for every brain voxels.
%
Hierarchical region-network sparsity addresses these shortcomings
by estimating individual voxel contributions
while benefitting from their functional segregation and integration
to restrict statistical complexity.
%
Viewed from the bias-variance tradeoff,
our modification to logistic regression estimators
entailed a large decrease in model variance but only a modest
increase in model bias.
Viewed from the Vapnik-Chervonenkis dimensions,
this entailed a healthy decrease in the complexity capacity of the prediction model
with a higher chance of generalizing to unobserved data.

In the future,
region-network sparsity priors could be incorporated into various
pattern-learning methods in systems neuroscience.
%
This includes supervised methods for whole-brain classification and regression
with one or several target variables.
The principled regularization scheme could inform
unsupervised structure-discovery by
matrix factorization and clustering algorithms
\cite{jenatton2009structured, witten2010framework}.
Additionally,
model regularization by hierarchical structured sparsity could be extended
from the spatial domain of neural activity to
priors of coherent spatiotemporal activity structure
\cite{gramfort2011tracking}.
%
The deterministic choice of a region and network atlas
could further be avoided by
sparse selection of overcomplete region-network dictionaries.
Non-hierarchical penalty terms will probably allow for
more complex structured sparsity that
extend the recently enabled parent-children dependencies.
%
Ultimately,
successful high-dimensional inference is
an important prerequisite
for predicting diagnosis,
disease trajectories, and treatment response
in personalized psychiatry and neurology.

>>>>

The present approach has important advantages over previous
analysis strategies that rely on dimensionality reduction of
the neuroimaging data to harness the curse of dimensionality.
They often resort to preliminary pooling functions within regions
or regression against network templates
for subsequent supervised learning on the aggregated feature space.
Such lossy approaches of
feature engineering and subsequent inference
\textit{i)} can only satisfy the specialization or
integration account of brain organization,
\textit{ii)} depend on the ground truth being a region or network effect,
and
\textit{iii)} cannot issue individual coefficients for every brain voxel.
%
Hierarchical region-network sparsity addresses these shortcomings
by estimating individual voxel contributions
while benefitting from their biological multi-level stratification
to restrict statistical complexity.
%
Viewed from the bias-variance tradeoff,
our modification to logistic regression
entailed a large decrease in model variance but only a modest
increase in model bias.
Viewed from the Vapnik-Chervonenkis dimensions,
this entailed a healthy decrease in the complexity capacity of the prediction model
with a higher chance of extrapolating to unobserved data samples.

In the future,
region-network sparsity priors could be incorporated into various
pattern-learning methods in systems neuroscience.
%
This includes supervised methods for whole-brain classification and regression
in single- and multi-task learning settings.
The principled regularization scheme could inform
unsupervised structure-discovery by
matrix factorization and clustering algorithms
\cite{jenatton2009structured, witten2010framework}.
Additionally,
hierarchical regularization could be extended
from the spatial activity domain to
priors of coherent spatiotemporal activity structure
\cite{gramfort2011tracking}.
%
The deterministic choice of a region and network atlas
could further be avoided by
sparse selection of overcomplete region-network dictionaries.
Advanced but non-hierarchical penalty terms will probably allow for
more complex structured sparsity that
go beyond the recently enabled parent-children dependencies.
%
Ultimately,
successful high-dimensional inference is
a prerequisite
for predicting diagnosis,
disease trajectories, and treatment response
in personalized psychiatry and neurology.
